Scikit-learn: machine learning without learning the machinery

### 2014-06-30 article.tex
Finish??

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code comes with a significant maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
comes to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to identify and integrate all major
methods that are most useful for prediction tasks. We favor time-tested
algorithms and put great care in the choice of default parameters. Our
secret ambition is that the documentation, that we strive to make
didactic and pragmatic, can provide an executable alternative to
textbooks, as all the figures are generated with code examples.

>>>>

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code, comes with a significant maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
came to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to identify and integrate all major
methods most useful for prediction tasks. We favor time-tested
algorithms and put great care in the choice of default parameters. Our
secret ambition is that the documentation, that we strive to make
didactic and pragmatic, can provide an executable alternative to
textbooks, with all the figures generated by code examples.
